---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%",
  fig.align = "center"
)
```

# Generation of Code Names for Organizations, People, Projects, and Whatever Else

```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

```{r, echo = FALSE, results='asis'}
cat(
	badge_cran_release("codename", "green"),
	badge_cran_download("codename", "grand-total", "green"),
	badge_cran_download("codename", "last-month", "green"),
	badge_cran_download("codename", "last-week", "green")
)
```

`codename` allows for users to create short, pithy code names for their organizations, their work projects, themselves, other people, or whatever else. The core of this package is the eponymous `codename()` function, which allows the user to create various types of code names. The code names returned from this function, by in large, are a two-word character vector of an attribute and an object. Right now, options include "any" (which is default and incorporates a battery of adjectives and nouns), "gods" (in which the object is the name of a deity or saint from some religion), "ubuntu" (in which the code name is alliterative but the object is always an animal), and "wu-tang" (in which the code name is derived from the classic Wu-Tang Name Generator). `codename()` also features the ability to use reproducible seeds, including character seeds, for maximum transparency and reproducibility.

# Installation

You will ideally soon be able to install this on CRAN, as follows:

```r
install.packages("codename")

```

Until then, you can install the development version of this package through the `devtools` package.

```r
devtools::install_github("svmiller/codename")
```

# Usage

There isn't much to belabor here and usage should be self-explanatory. Here is some sample output.

```{r}
library(codename)

message(paste0("code name generated by {codename} v.", packageVersion("codename")))

# defaults to any
codename()
codename()
codename()
codename(seed = 8675309)
codename(seed = "My Project Name: The Subtitle of It Too")

codename(type = "gods")
codename(type = "gods")
codename(type = "gods")
codename(type = "gods", seed = 8675309)



codename(type = "ubuntu")
codename(type = "ubuntu")
codename(type = "ubuntu")
codename(type = "ubuntu", seed = 8675309)
codename(type = "ubuntu", seed = 8675309)
codename(type = "ubuntu", seed = "My Ubuntu Release")

codename(type = "wu-tang")
codename(type = "wu-tang")
codename(type = "wu-tang", seed = "Steven V. Miller")

all_types <- c("any", "gods", "ubuntu", "wu-tang")

for (i in all_types) {
  output <- codename(type = i, seed  = "A Reproducible Character Seed")
  print(output)
}

```


# Hall of Fame Entries

This is an incomplete and running list of some of my favorite returns from this function. Because most of the sample output on the README is a one-off return, these are prone to disappear every time the README is updated. No matter, I want to preserve some of these, for posterity.

- electric lime agenda
- second-hand shovel
